---
title: "DSC 385 - Project 1 Report"
format: html
---

## Name and EID

Please enter your name and EID here.

## Setup

```{r setup}
#| include: false

## Load the tidyverse package
library(tidyverse)

## If you need to load other packages, place that code below here.
```

```{r}
#| message: false

## Loading all the data files
## DO NOT CHANGE THIS CODE
championships <- read_tsv("WCA_export_championships.tsv.bz2")
competitions <- read_tsv("WCA_export_Competitions.tsv.bz2")
continents <- read_tsv("WCA_export_Continents.tsv.bz2")
countries <- read_tsv("WCA_export_Countries.tsv.bz2")
eligible_country_iso2s_for_championship <- read_tsv("WCA_export_eligible_country_iso2s_for_championship.tsv.bz2")
events <- read_tsv("WCA_export_Events.tsv.bz2")
formats <- read_tsv("WCA_export_Formats.tsv.bz2")
persons <- read_tsv("WCA_export_Persons.tsv.bz2")
ranksaverage <- read_tsv("WCA_export_RanksAverage_333.tsv.bz2")
rankssingle <- read_tsv("WCA_export_RanksSingle_333.tsv.bz2")
results <- read_tsv("WCA_export_Results_333.tsv.bz2")
roundtypes <- read_tsv("WCA_export_RoundTypes.tsv.bz2")
scrambles <- read_tsv("WCA_export_Scrambles.tsv.bz2")
```


## Required Questions

### Active Speed Cubers

How many active (3x3x3) speedcubers are there registered with the WCA? 

For this question an *active speeedcuber* is defined as any person registered in the WCA who has competed in at least two competitions in the years 2022--2024. 


```{r}
## Add your code here

```

**Write your answer here.**



### World Records

This question has two parts:

1. According to the data, who holds the world record single best solve? On what date was this record set? 


```{r}
## Add your code here

```

**Write your answer here.**

On what date was this record set?

```{r}
## Add your code here

```

**Write your answer here.**



2. According to the data, who previously held the world record best single solve? 

```{r}
## Add your code here

```


**Write your answer here.**

On what date was this previous record set?

```{r}
## Add your code here

```

**Write your answer here.**


NOTE: For these questions, consider all speedcubers (not just active ones) and define "best" as the fastest time for a single solve (not for an average).



### Regional Rankings

This question has two parts:

1. Amongst all speedcubers, who is the top ranked male speedcuber (for best single solve) in Australia?

```{r}
## Add your code here

```

**Write your answer here.**




2. Amongst all speedcubers, who is the top ranked female speedcuber (for best single solve time) in Europe?

NOTE: Europe is identified under the `continentId` column of the `countries` table.


```{r}
## Add your code here

```



**Write your answer here.**




### Time Until Sub-5

Having a time below 5 seconds is considered an elite achievement and most speedcubers have to complete a large number of solves before they can obtain a sub-5 second solve. 

1. For the current top 10 speedcubers in the world (as recorded in the `RanksSingle` table), on average, how many solves did they have to do before achieving a sub-5 second solve?

**NOTE**: Each round of a competition has 5 solves that should be considered separately when counting the number of solves.


```{r}
## Add your code here

```

**Write your answer here.**




2. For **one** of the top 10 speedcubers make a scatterplot of their individual single solve times vs. the date of the solve, with date on the x-axis and solve time on the y-axis. 


```{r}
## Add your code here

```


### Up-and-Coming Speed Cubers

Which speed cubers **not** in the top 10,000 (worldwide for single best time) should we keep an eye on for the near future? 

The idea here is to identify "up-and-coming" speedcubers who are not yet achieving elite times. Come up with a list of **five** speedcubers (provide their names and WCA IDs) that you have identified as "up-and-coming". There is no one way to answer this question and the goal is to provide an analysis of the data that justifies the selection of your five names.

```{r}
## Add your code here

```

**Write your result here.**




## Discussion

